Conference Paper Title*

### 2020-03-15 paper.tex
Remove unused line

%\thanks{Identify applicable funding agency here. If none, delete this.}{
%}

@@

\begin{IEEEkeywords}
privacy computing, crowd sensing, data marketplace, decentralization
\end{IEEEkeywords}

@@

\section{Conclusions}
By combining the established standards and openly-developed specifications, this paper proposed an autonomous data marketplace design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services. It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants and enable secure communication and flexible trading mechanisms.

%\section*{Acknowledgment}

>>>>

@@

\begin{IEEEkeywords}
privacy computing, crowd sensing, publish/subscribe, decentralization
\end{IEEEkeywords}

@@

\section{Conclusions}
By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services. It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants and enable secure communication and flexible trading mechanisms.
